### 2016-11-22 local-capability-machine.tex
Added clear macro instruction
Added note on the use of call, scall and the use of a combination of the two

@@

>>>>

\item[\texttt{clear $r$}] Clears all cells $r$ has authority over. 

@@

\item If we want to have local capabilities as part of our private state, then we need to have a stack and use \texttt{scall}. If we do not have any local capabilities we want to keep around, then we can use \texttt{call}, but it will incur a small memory leak as the activation records cannot be recycled! It is also possible to use a combination of \texttt{scall} and \texttt{call}, but when \texttt{call} is used, then we have no way to store the stack, so we cannot use \texttt{scall} after that.
